Reputational Risk and Questionable Research Practices in Archaeological Science

### 2023-10-07 docs/paper.qmd
add statcheck results

@@

@@

@@

>>>>

jasr_relative_risk <- 
  jasr_caliper_test_binom_test$estimate[[1]] / jasr_caliper_test_binom_test$null.value[[1]]

@@

jas_relative_risk <- 
  jas_caliper_test_binom_test$estimate[[1]] / jas_caliper_test_binom_test$null.value[[1]]

@@

The JAS p-value is `r format(jas_caliper_p, scientific = FALSE)` and the JASR p-value is `r format(jasr_caliper_p, scientific = FALSE)`

@@

## Statcheck of JASR articles

library(statcheck)

# load articles -------------------------------------------------------------
full_text_jasr_statcheck <- readRDS("data/full_text_jasr.rds")

# run statcheck
jasr_statcheck_results <- 
  full_text_jasr_statcheck %>% 
  mutate(statcheck_results = map(unlist(full_text_jasr), statcheck))

jasr_statcheck_results %>% 
  select(-full_text_jasr) %>%  
  unnest(statcheck_results) %>% View

# plot it
jasr_statcheck_results_tbl <- 
  jasr_statcheck_results %>% 
  select(statcheck_results) %>% 
  unnest()

class(jasr_statcheck_results_tbl) <- c("statcheck", "data.frame")
plot(jasr_statcheck_results_tbl, APAstyle = TRUE) +
  geom_point(size = 4) +
  scale_color_viridis_d()
```

## Statcheck of JAS articles

```{r}
# load articles -------------------------------------------------------------
full_text_jas_statcheck <- readRDS("data/full_text_jas.rds")

# run statcheck
jas_statcheck_results <- 
  full_text_jas_statcheck %>% 
  mutate(statcheck_results = map(unlist(full_text_jas), statcheck))

jas_statcheck_results %>% 
  select(-full_text_jas) %>%  
  unnest(statcheck_results)

# plot it
jas_statcheck_results_tbl <- 
  jas_statcheck_results %>% 
  select(statcheck_results) %>% 
  unnest()

class(jas_statcheck_results_tbl) <- c("statcheck", "data.frame")
plot(jas_statcheck_results_tbl, APAstyle = TRUE)
```
